---
title: "RWorksheet_CAHUYA#6"
author: "CAHUYA, CARLO J'NAED LYTON BSIT-2A"
date: "2022-11-23"
output: pdf_document
---

```{r, vector = TRUE}
library(dplyr)
library(ggplot2)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\hfill\break
1. How many columns are in mpg data set? How about the number of rows? Show the codes and its result.
```{r, vector = TRUE}
data(mpg)
mpg_data <- glimpse(mpg)
mpg_data 
nrow(mpg)
ncol(mpg)
# The mpg data set have 11 columns and 234 rows. 
```
\hfill\break

2. Which manufacturer has the most models in this data set? 
```{r, vector = TRUE}
most_mods <- mpg_data %>% group_by(manufacturer) %>% count()
most_mods
colnames(most_mods) <- c("Manufacturer","Counts")
most_mods
#  Dodge has the most number of models. It has 37 models.
```
Which model has the most variations?
```{r, vector = TRUE}
most_var<- mpg_data %>% group_by(model) %>% count()
most_var
colnames(most_var) <- c("Model","Counts")
most_var
# Caravan 2wd model has the most variations. It has 11 variations.
```
a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r, vector = TRUE}
unique_mods<- mpg_data %>% group_by(manufacturer, model) %>% distinct() %>% count()
unique_mods
colnames(unique_mods) <- c("Manufacturer", "Model","Counts")
unique_mods
```
b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r, vector = TRUE}
plot(unique_mods)
```

```{r, vector = TRUE}
ggplot(unique_mods, aes(x = Model, y = Counts )) + geom_point(color='black')
```
\hfill\break

3. Same dataset will be used. You are going to show the relationship of the model 
and the manufacturer.

```{r, vector = TRUE}
ggplot(unique_mods, aes(x = Model, y = Manufacturer )) + geom_point(color='black')
```

a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r, vector = TRUE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
# The output of the code displays a plot with black points in it.
```
b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r, vector = TRUE}
# Yes, it is helpful since you can trace down the data for each model from the manufacturers.
```
\hfill\break
4. Using the pipe (%>%), group the model and get the number of cars per model.
 Show codes and its result.
```{r, vector = TRUE}
car_mods <- mpg_data %>% group_by(model) %>% count()
car_mods
colnames(car_mods) <- c("Model","Counts")
car_mods
```
a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r, vector = TRUE}
bar_graph <- ggplot(car_mods, aes( x = Model, y = Counts, fill = Model)) + 
  labs(title = "Numbers of cars per Model", y = "Number of Cars", x = "Model")  +
  geom_bar(stat = "identity") + theme(legend.position = "none")
bar_graph +
  coord_flip()
           
```
 b. Use only the top 20 observations. Show code and results.
```{r, vector = TRUE}
head(car_mods, n = 20)
```
\hfill\break
5. Plot the relationship between cyl - number of cylinders and displ - engine displacement 
using geom_point with aesthetic colour = engine displacement. Title should be 
“Relationship between No. of Cylinders and Engine Displacement”.
a. Show the codes and its result.
```{r, vector = TRUE}
qplot(model,data = mpg,main = "Number of Cars per Model", xlab = "Model",
      ylab = "Number of Cars", geom = "bar", fill = manufacturer) + coord_flip()
```
b. How would you describe its relationship?

```{r, vector = TRUE}
# Based on the output of the code, I can say that their connection is very consistent or stable.
```
\hfill\break
6. Get the total number of observations for drv - type of drive train (f = front-wheel drive, 
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).
```{r, vector = TRUE}
ggplot(data = mpg_data, mapping = aes(x = drv, y = class)) +
  geom_tile(aes(fill=class))
```
Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.
a. Show the codes and its result for the narrative in #6.
```{r, vector = TRUE}
ggplot(mpg, aes(drv, class)) +
  geom_tile (aes(fill = class)) 
```
b. Interpret the result.
```{r, vector = TRUE}
# The mapping geometric point graph is used to "map" the black areas.
# The output shows that if there is a relationship between a class and drv, a tile is created. 
```
\hfill\break
7. Discuss the difference between these codes. Its outputs for each are shown below.
```{r,echo=TRUE}
#Code#1
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

```{r,echo=TRUE}
#Code#2
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```

```{r, vector = TRUE}
# The "colour = blue" code in the first code was inside the function aes(), so it failed to add 
# black dots or points. The second code, on the other hand, was performed and was in its right 
# location or outside the aes() method, and the plot was shown accordingly.
```
\hfill\break
8. Try to run the command ?mpg. What is the result of this command?
```{r, vector = TRUE}
?mpg
# It shows "Fuel economy data from 1999 to 2008 for 38 popular models of cars" in the help panel.
```
a. Which variables from mpg data set are categorical?
- Categorical variables in mpg include: manufacturer, model, trans (type of transmission), 
drv (front-wheel drive, rear-wheel, 4wd), fi (fuel type), and class (type of car)

b. Which are continuous variables?
- Continuous variables in mpg include: displ (engine displacement in litres), cyl 
 (number of cylinders), cty (city miles/gallon), and hwy (highway gallons/mile)

c. Plot the relationship between displ (engine displacement) and hwy(highway miles
 per gallon). Mapped it with a continuous variable you have identified in 5-b. 
 What is its result? Why it produced such output?
```{r, vector = TRUE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ , y = hwy, col = displ)) 
```

  
```{r, vector = TRUE}
# It produced such output because we plot the relationship between the displ and hwy and its geom_point color should be mapped in with a continuous variable.
```
\hfill\break
9. Plot the relationship between displ (engine displacement) and hwy(highway miles
 per gallon) using geom_point(). Add a trend line over the existing plot using
  geom_smooth() with se = FALSE. Default method is “loess”.
```{r, vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=displ)) +
  geom_smooth(se =FALSE)
```
\hfill\break
10. Using the relationship of displ and hwy, add a trend line over existing plot. Set the
se = FALSE to remove the confidence interval and method = lm to check for linear modeling.
```{r, vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=displ)) +
  geom_smooth(se =FALSE,method = lm)
```