---
title: "RWorksheet_CAHUYA#7"
author: "CAHUYA, CARLO J'NAED LYTON BSIT-2A"
date: "2022-12-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, vector = TRUE}
library(Hmisc)
library(pastecs)
```
\hfill\break
Basic StatisticS
1. Create a data frame for the table below.
```{r, vector = TRUE}
scores <- data.frame(
  Student = seq(1:10),
  Pre_test = c(55, 54, 47, 57, 51, 61, 57, 54, 63, 58),
  post_test = c(61, 60, 56, 63, 56, 63, 59, 56, 62, 61)
)
scores
colnames(scores) <- c("Student", "Pre-test", "Post-test")
scores
```
a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.
HMISC
```{r, vector = TRUE}
dsHmisc <- describe(scores)
dsHmisc
```
PASTECS
```{r, vector = TRUE}
dsPastecs <- stat.desc(scores)
dsPastecs
```
\hfill\break
2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.The data were 10,10,10, 20,20,50,10,20,10,50,20,50,20,10.
```{r, vector = TRUE}
data <- c(10,10,10, 20,20,50,10,20,10,50,20,50,20,10)
```
a. Write the codes and describe the result
```{r, vector = TRUE}
factor(data)
sort(data, decreasing = FALSE)
#The result displays the differerent levels of fertilizer in an ordered or increasing manner.
```
\hfill\break
3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense
```{r, vector = TRUE}
exer_levels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")
```
a. What is the best way to represent this in R?
```{r, vector = TRUE}
exer_levels
factor(exer_levels)
# Data.frame is the best way to represent them.
```
\hfill\break
4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:
```{r, vector = TRUE}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
state
```
a. Apply the factor function and factor level. Describe the results.
```{r, vector = TRUE}
factorState <- factor(state)
factorState
factorLevel <- levels(factorState)
factorLevel
#The vector and its levels are shown using the factor() function.
#The levels() function simply displays the different levels or characters that have been utilized.
```
\hfill\break
5. From #4 - continuation:
Suppose we have the incomes of the same tax accountants in another vector (in suitably large units of money)
```{r, vector = TRUE}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61,
             61, 58,51, 48,  65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
incomes
```
```{r, vector = TRUE}
total_data <- data.frame(
  state = c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
            "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
            "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
            "vic", "vic", "act"),
  incomes = c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61,
              61, 58,51, 48,  65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
)
total_data
```
a. Calculate the sample mean income for each state we can now use the special
function tapply():
```{r, vector = TRUE}
tapply(incomes, state, mean)
```
b. Copy the results and interpret.
```{r, vector = TRUE}
tapply(incomes, state, mean)
# It displays the levels of the vector and their corresponding mean.
```
\hfill\break
6. Calculate the standard errors of the state income means (refer again to number 3)
a. What is the standard error? Write the codes.
```{r, vector = TRUE}
stdError <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, state, stdError)
incster
```
b. Interpret the result.
```{r, vector = TRUE}
# The output shows the standard deviation of the sample distribution or an estimate of the SE. 
# It shows the levels as well as the related SD.
```

\hfill\break
7. Use the titanic dataset.
```{r, vector = TRUE}
data("Titanic")
titanic_DF <- as.data.frame(Titanic)
titanic_DF
```
a. subset the titanic dataset of those who survived and not survived. Show the
codes and its result.
\hfill\break
SURVIVED
```{r, vector = TRUE}
survived_sub <- subset(titanic_DF , Survived == 'Yes')
survived_sub
```
\hfill\break
NOT SURVIVED
```{r, vector = TRUE}
not_survived_sub <- subset(titanic_DF , Survived == 'No')
not_survived_sub
```
\hfill\break
8. The data sets are about the breast cancer Wisconsin. The samples arrive periodiically as Dr. Wolberg reports his clinical cases. The database therefore reflects this chronological grouping of the data. You can create this dataset in Microsoft Excel.
```{r, vector = TRUE}
library("readxl")
Breast_Cancer <- read_excel("C:/Data_Science/Worksheet7/Breast_Cancer.xlsx")
Breast_Cancer
```

a. describe what is the dataset all about.
```{r, vector = TRUE}
# The dataset contains information on breast cancer clinical cases such as CL thickness, Cell size, Cell shape, Marg,Adhesion, Epith. C.size, Bare. Nuclei, Bl. Cromatin, Normal nucleoli, Mitoses, and Class.
```

b. Import the data from MS Excel. Copy the codes.
```{r, vector = TRUE}
Breast_Cancer <- read_excel("C:/Data_Science/Worksheet7/Breast_Cancer.xlsx")
Breast_Cancer
```

c. Compute the descriptive statistics using different packages. Find the values of:
c.1 Standard error of the mean for clump thickness.
```{r, vector = TRUE}
standard_clump <- sd(Breast_Cancer$`CL. thickness`/sqrt(length((Breast_Cancer$`CL. thickness`))))
standard_clump
```

c.2 Coefficient of variability for Marginal Adhesion.
```{r, vector = TRUE}
cv_marg_adhesion <- sd(Breast_Cancer$`Marg. Adhesion`) / mean(Breast_Cancer$`Marg. Adhesion`) * 100
cv_marg_adhesion 
```
c.3 Number of null values of Bare Nuclei.
```{r, vector = TRUE}
num_bare_nuclei <- sum(is.na(Breast_Cancer$`Bare. Nuclei`))
num_bare_nuclei
```
c.4 Mean and standard deviation for Bland Chromatin
```{r, vector = TRUE}
mean_B_chromatin <- mean(Breast_Cancer$`Bl. Cromatin`)
mean_B_chromatin 

standard_dev_B_chromatin <- sd(Breast_Cancer$`Bl. Cromatin`)
standard_dev_B_chromatin 
```
c.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r, vector = TRUE}
mean_cell <- mean(Breast_Cancer$`Cell Shape`)
standard_cell <- sd(Breast_Cancer$`Cell Shape`)/sqrt(length(Breast_Cancer$`Cell Shape`))

alpha <- 0.05
dg <- length(Breast_Cancer$`Cell Shape`) - 1

t.score <- qt(p = alpha/2 , df = dg, lower.tail = F)

margin.error <- t.score * standard_cell
lower.bound <- mean_cell - margin.error
upper.bound <- mean_cell + margin.error

CFinterval <- c(lower.bound, upper.bound)
CFinterval
```

d. How many attributes?
```{r, vector = TRUE}
# Null
```

e. Find the percentage of respondents who are malignant. Interpret the results.
```{r, vector = TRUE}
library(dplyr ) 
Breast_Cancer %>%
  group_by(Class) %>% 
  summarise( Percent = 100 * n() / nrow(Breast_Cancer))
```
\hfill\break
9. Export the data abalone to the Microsoft excel file. Copy the codes.
install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")
view(abalone)
head(abalone)
summary(abalone)

```{r, vector = TRUE}
library("AppliedPredictiveModeling")
data(abalone)
head(abalone)
summary(abalone)
```