---
title: "RWorksheet_CAHUYA#3B"
author: "CAHUYA, CARLO J'NAED LYTON BSIT-2A"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\hfill\break
1.Create a data frame using the table below.

a. Write the codes.
```{r, vector = TRUE}
Table1 <- data.frame(
  Respondents = seq(1:20),
  Sex = rep(c(2,1,2,1,2,1,2),c(2,1,7,1,7,1,1)),
  Fathers_Occupation = c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1),
  Persons_Home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
  Siblings_School= c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
  Houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
)                      
Table1
names(Table1) <- list("Respondents","Sex","Fathers Occupation","Persons at Home",
                      "Siblings at school","Types of houses")
Table1 
```
\hfill\break
b. Describe the data. Get the structure or the summary of the data
```{r, vector = TRUE}
#Sex, Respondents, Persons at Home, Types of Houses, Fathers Occupation, and Siblings in School displays data with numbers, and each number corresponds to a value and those values are also known as their legends.
summary(Table1)
```
\hfill\break
c. Is the mean number of siblings attending is 5?
```{r, vector = TRUE}
# No it is not. 2.95 is the Mean of the number of siblings attending.
```
\hfill\break
d. Extract the 1st two rows and then all the columns using the subsetting functions.
 Write the codes and its output.
```{r, vector = TRUE}
subset_1 <- subset(Table1[1:2,])                                      
subset_1 
```
\hfill\break
e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and itsresult.   

```{r, vector = TRUE}
subset_2 <- subset(Table1[c( 3, 5 ),c(2,4)])
subset_2
```
\hfill\break
f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.
```{r, vector = TRUE}
types_houses <- c(Table1$`Types of houses`)                    
types_houses 
```
\hfill\break
g. Select only all Males respondent that their father occupation was farmer. 
Write the codes and its output.
```{r, vector = TRUE}
Table2 <- data.frame(
  Respondents = seq(1:20),
  Sex = rep(c(2,1,2,1,2,1,2),c(2,1,7,1,7,1,1)),
  Fathers_Occupation = c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1),
  Persons_Home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
  Siblings_School= c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
  Houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
)                      
Table2

Male_Farm <- subset(Table2, Sex == '1' & Fathers_Occupation == '1')
Male_Farm_Names <- Male_Farm[c(2,3)]
Male_Farm_Names
```
\hfill\break
h. Select only all females respondent that have greater than or equal to 5 number
of siblings attending school. Write the codes and its outputs  
```{r, vector = TRUE}
Male_Farm2 <- subset(Table2,Sex == '2' & Siblings_School >= '5')
Male_Farm_Names2 <- Male_Farm2[c(2,5)]
Male_Farm_Names2 
```
\hfill\break
2. Write a R program to create an empty data frame. Using the following codes:
  
```{r, vector = TRUE}
df = data.frame(Ints=integer(),
                  Doubles=double(), Characters=character(),
                  Logicals=logical(),
                  Factors=factor(),
                  stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```
\hfill\break
a. Describe the results.
```{r, vector = TRUE}
# The output shows the internal structure of the 'df' data frame. 
# It indicates that the data frame's structure is null or empty.
```
\hfill\break
3. Interpret the graph.
```{r, vector = TRUE}
# The chart illustrates that Donald Trump has far more negative tweet sentiments 
# than positive tweet sentiments on a daily basis and there are also significantly 
# less neutral sentiments compared to positive and negative tweets.
```